Towards a classification framework for social machines

### 2013-02-24 latex/paper_new.tex
working on 4.3

\begin{table}[htb]
\begin{center}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Users and Roles} \\
\hline
Generality of Audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles/responsibilities among participants \\
\hline
{\bf Tasks} \\
\hline
Task involves creative production or creation of content \\
Task involves subjective appraisal of content \\
Task solves (a defnable) computation problem/set of problems\\
Domain-specificity of tasks \\
Service/platform derives benefit from participation \\
Variation in types of contributions and tasks \\
{\bf Motivation} \\
Participants are intrinsically motivated:\\
\hspace{1cm} to gain/share knowledge \\
\hspace{1cm} to ``get something done'' \\
\hspace{1cm} to ``for fun/entertainment''\\
\hspace{1cm} to ``be social'' \\
Participation is motivated by extrinsic reward (payment, status etc) \\
Participation is done for the benefit of a specific third-party \\
Participation is done for the benefit of society as a whole \\
\hline
{\bf Context of Participation} \\
\hline
Participants' (geographic) location is relevant to the service \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hline
\end{tabular}
\end{center}
\caption{Consolidated constructs of social machines.} \label{table:constructs}
\end{table}

>>>>

\begin{table}[htb]
\begin{center}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Users and Roles} \\
\hline
Generality of Audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles/responsibilities among participants \\
\hline
{\bf Tasks} \\
\hline
Task involves creative production or creation of content \\
Task involves subjective appraisal of content \\
Task solves (a defnable) computation problem/set of problems\\
Domain-specificity of tasks \\
Service/platform derives benefit from participation \\
Variation in types of contributions and tasks \\
\hline
{\bf Motivation} \\
\hline
Participants are intrinsically motivated:\\
\hspace{1cm} to gain/share knowledge \\
\hspace{1cm} to ``get something done'' \\
\hspace{1cm} to ``for fun/entertainment''\\
\hspace{1cm} to ``be social'' \\
Participation is motivated by extrinsic reward (payment, status etc) \\
Participation is done for the benefit of a specific third-party \\
Participation is done for the benefit of society as a whole \\
\hline
{\bf Context of Participation} \\
\hline
Participants' (geographic) location is relevant to the service \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hline
\end{tabular}
\end{center}
\caption{Consolidated constructs of social machines.} \label{table:constructs}
\end{table}
